Thesis: draft

### 2021-05-06 draft.tex
latest update: worked on discussion

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
    \caption{Last.fm}
    \includegraphics[width=8cm, height=7cm]{lastfm_degree_distribution_8x7.png}
    \label{deg_distr_lastfm}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \caption{PGP}
    \includegraphics[width=8cm, height=7cm]{PGP_degree_distribution_8x7.png}
    \label{deg_distr_pgp}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Degree distribution $P(k)$ of the two real-world networks used in this thesis.]{Degree distribution $P(k)$ of the two real-world networks used in this thesis. \textbf{(a)} Last.fm on-line social network with a log-normal fit ($\mu = 1.0078272$, $\sigma = 0.95173779$); \textbf{(b)} PGP on-line trust network with two power-law fits ($a = 0.39604951$, $\gamma = 1.53568449$ for $k < 20$ and $a = 5.59021251$, $\gamma = 2.4944057$ for $k \geqslant 20$).}
\label{ev_op_50_50}
\end{figure}

% Discuss actual networks we used!! + reference them??

@@

The formation of echo chambers versus the fraction of completely stubborn actors, fracRes, in the Last.fm on-line social network is studied. The results are compared to corresponding results from network models, all with $N = 8003$: (i) the Watts-Strogatz model with $\left<k\right> = 4$, $\beta = 0.15$ and $\left<cc\right> = 0.317 \pm 0.004$; (ii) the stochastic block model with 53 communities of size 151, $p_\text{cl} = 0.023$, $p_\text{add} = 0.0001$, $\left<k\right> = 4.24 \pm 0.03$ and $Q = 0.811 \pm 0.004$; (iii) the stochastic Watts-Strogatz block model with 53 communities of size 151, each community has the following Watts-Strogatz parameters: $\left<k\right> = 4$, $\beta = 0.025$; edges are added between communities with probability $p_\text{add} = 0.0001$, $\left<k\right> = 4.77 \pm 0.01$, $\left<cc\right> = 0.344 \pm 0.002$ and $Q = 0.833 \pm 0.003$. The results for the PR and REC filtering algorithm are shown in Fig. \ref{echo_vs_fracRes_real}.

@@

For the PR filtering algorithm, the randomly distributed scenario resulted in an increase in the formation of echo chambers around the majority opinion A. This was observed for both the low and high modularity networks. The community distributed scenario for the low modularity network hampers this increase. It was found that this is more than just a result of the increased number of initial opinion A echo chambers. For the high modularity network, the community distributed scenario showed an even larger hampering of the formation of echo chambers around the majority opinion A. This is probably the result of: (i) an even higher initial number of echo chambers around the majority opinion A than for the low modularity network; (ii) the hampering in the increase in the majority opinion A for the community distributed scenario in case of the high modularity network combined with the PR filtering algorithm. 
% talk about echo chambers??

>>>>

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
    \caption{Last.fm}
    \includegraphics[width=8cm, height=7cm]{lastfm_degree_distribution_8x7.png}
    \label{deg_distr_lastfm}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \caption{PGP}
    \includegraphics[width=8cm, height=7cm]{PGP_degree_distribution_8x7.png}
    \label{deg_distr_pgp}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Degree distribution $P(k)$ of the two real-world networks used in this thesis.]{Degree distribution $P(k)$ of the two real-world networks used in this thesis. \textbf{(a)} Last.fm on-line social network with a log-normal fit ($\mu = 1.0078272$, $\sigma = 0.95173779$); \textbf{(b)} PGP on-line trust network with two power-law fits ($a = 0.39604951$, $\gamma = 1.53568449$ for $k < 20$ and $a = 5.59021251$, $\gamma = 2.4944057$ for $k \geqslant 20$).}
\label{deg_distr_real_network}
\end{figure}

@@

The formation of echo chambers versus the fraction of completely stubborn actors, fracRes, in the Last.fm on-line social network is studied. The results are compared to corresponding results from network models, all with $N = 8003$: (i) the Watts-Strogatz model with $\left<k\right> = 4$, $\beta = 0.15$ and $\left<cc\right> = 0.317 \pm 0.004$; (ii) the stochastic block model with 53 communities of size 151, $p_\text{cl} = 0.023$, $p_\text{add} = 0.0001$, $\left<k\right> = 4.24 \pm 0.03$ and $Q = 0.811 \pm 0.004$; (iii) the stochastic Watts-Strogatz block model with 53 communities of size 151, each community has the following Watts-Strogatz parameters: $\left<k\right> = 4$, $\beta = 0.025$; edges are added between communities with probability $p_\text{add} = 0.0001$, $\left<k\right> = 4.77 \pm 0.01$, $\left<cc\right> = 0.344 \pm 0.002$ and $Q = 0.833 \pm 0.003$. The results for the PR and REC filtering algorithm are shown in Fig. \ref{echo_vs_fracRes_real}.\\
\newline
The PR filtering algorithm shows a decrease in the formation of echo chambers with an increasing fraction of stubborn actors. This is valid for both the real-world network and the network models. The stochastic Watts-Strogatz block model has a similar clustering and community structure as the Last.fm network. The Last.fm network has, however, a smaller formation of echo chambers than the SBM-WS. This suggests that it is not only the clustering and/or the community structure that drives the formation of echo chambers. Other topologies must play a role as well. The biggest difference between the real-world Last.fm network and the stochastic Watts-Strogatz block model lies in the degree distribution: the Last.fm network has a heterogeneous degree distribution instead of a homogeneous. It is probably this heterogeneous contact pattern that hampers the formation of echo chambers in the real-world network compared to a network model with similar clustering and modularity, but with a homogeneous degree distribution.

@@

For the PR filtering algorithm, the randomly distributed scenario resulted in an increase in the formation of echo chambers around the majority opinion A. This was observed for both the low and high modularity networks. The community distributed scenario for the low modularity network hampers this increase. It was found that this is more than just a result of the increased number of initial opinion A echo chambers. For the high modularity network, the community distributed scenario showed an even larger hampering of the formation of echo chambers around the majority opinion A. This is probably the result of: (i) an even higher initial number of echo chambers around the majority opinion A than for the low modularity network; (ii) the hampering in the increase in the majority opinion A for the community distributed scenario in case of the high modularity network combined with the PR filtering algorithm. \\
% summarize real-world network results
The formation of echo chambers, and the enhancement of them when using algorithmic personalization such as semantic filtering, agrees with results found in literature \cite{Cinelli2020}\cite{Nikolov2015}. The enhancement of the formation of echo chambers in clustered communities is also found in literature on complex contagious processes \cite{Becker2017}.\\
The hampering in the increase of the majority opinion in case of unbalanced starting conditions combined with the introduction of stubborn actors for the PR filtering algorithm agrees partly with related research on continuous opinion dynamics models combined with stubborn actors \cite{Como2013}. In this research, Acemo\u{g}lu et al. showed that introducing stubborn actors (with different opinions) in an inhomogeneous stochastic gossip process of continuous opinion dynamics leads to a situation in which consensus can no longer be reached \cite{Como2013}. This result is also found in the majority opinion dynamics model and in the voter model combined with stubborn actors (equally distributed over the two opinions) \cite{Galam2007}\cite{Mobilia2007}\cite{Yildiz2013}. In our case, the possible consensus around the majority opinion, that could have been reached when combining the PR filtering algorithm with unbalanced starting conditions, can no longer be obtained when introducing stubborn actors.
